Tabular Constraint Learning

### 2016-04-08 Paper/ECAI/tabular.tex

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

@@

@@

\newcommand{\CName}{Name\xspace}
\newcommand{\CSignature}{Signature\xspace}
\newcommand{\CFunction}{Function\xspace}

@@

\section{Problem Statement}

>>>>

\documentclass{ecai}
\usepackage{times}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[numbers]{natbib}
\usepackage{notoccite}
\usepackage{framed}

@@

\newcommand{\CName}{Name\xspace}
\newcommand{\CSignature}{Signature\xspace}
\newcommand{\CFunction}{Function\xspace}
\newcommand{\dependecies}{\ensuremath{\mathcal{D}}\xspace}
\newcommand{\groups}{\ensuremath{\mathcal{G}}\xspace}

@@

@@

\section{Problem Statement}
In the previous section we introduced the problem of tabular constraint learning informally using the example in Figure \ref{fig:main_example}. Here we formalize the statement in terms of Excel constraints and group assignments.

\begin{framed}
  \begin{tabular}{ll}

    \multicolumn{2}{c}{{\textbf{Tabular Constraint Learning Problem}}}\\
    &\\
    \textbf{Given:} & The set of all groups $\groups$ and the set of Excel  \\
    \phantom{Given:} & constraints $\constraints$ with its dependencies DAG $\dependecies$\\
    \textbf{Find: } & text
  \end{tabular}
\end{framed}
